Lightning Talk: Software Citation: Process, Principles, and Implementation

### 2016-08-04 meetings/WSSSPE4-lightning-talk/WSSSPE4-lightning-talk.tex
small edit for -- adding ack fixing last bib entry spacing

\usepackage{flushend} % equalizes columns on last page

@@

The authors would like to thank...

>>>>

\usepackage[keeplastbox]{flushend} % equalizes columns on last page

@@

The authors would like to thank all members of the FORCE11 Software Citation Group (listed in~\cite{bib3}), the members of the FORCE11 executive committee for suggesting this activity and supporting our work on it, and the WSSSPE community (\url{http://wssspe.researchcomputing.org.uk}) for also suggesting this activity and providing a group of active participants over 3 meetings and the set of FORCE11 working group activities.
